Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-10-04 manuscript.Rmd
Added experiment 2 results write up

A similar process was adopted for the analysis of the pupillometry data. The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software [@Kassner2014]. The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted. Fourier transform was calculated for each waveform, and the spectrum stored in a matrix. All repetitions of each condition were then averaged for each eye. They were then averaged across the two eyes, to obtain individual results. Finally, these were averaged across all participants to obtain the final results.

@@

Figure \@ref(fig:pupildata) is showing the results for the pupillometry. Figure \@ref(fig:pupildata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:pupildata)b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli. Figures \@ref(fig:pupildata)c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz. In the same-frequency condition at 2 Hz (fig. \@ref(fig:pupildata)c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration. In the cross-frequency condtion at 2 Hz (fig. \@ref(fig:pupildata)d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition. Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig. \@ref(fig:pupildata)e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels. This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils. Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.

Figure \@ref(fig:EEGdata) shows the results for EEG. Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic. What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig. \@ref(fig:EEGdata)c) and second (fig. \@ref(fig:EEGdata)f) harmonic are showing very high summation of binocular signals. The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses. This is especially clear at the highest contrasts. For the cross-frequency condition at 2 Hz and 4 Hz (fig. \@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig. \@ref(fig:EEGdata)e) and 3.2 Hz (fig. \@ref(fig:EEGdata)h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex. 
```{r include=FALSE, results='hide'}

@@

## Experiment 2
The results from the second experiment are shown in figure \@ref(fig:TFdata). Figure \@ref(fig:TFdata)a is showing the fourier spectra
```{r include=FALSE, results='hide'}

>>>>

A similar process was adopted for the analysis of the pupillometry data. The data were converted from the mp4 format to a  csv text file using the Pupil Player software [@Kassner2014]. The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted. Fourier transform was calculated for each waveform, and the spectrum stored in a matrix. All repetitions of each condition were then averaged for each eye. They were then averaged across the two eyes, to obtain individual results. Finally, these were averaged across all participants to obtain the final results.

@@

Figure \@ref(fig:pupildata) is showing the results for the pupillometry. Figure \@ref(fig:pupildata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:pupildata)b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli. Figures \@ref(fig:pupildata)c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz. In the same-frequency condition at 2 Hz (fig. \@ref(fig:pupildata)c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration. In general, we observe that the binocular to monocular ratio is roughly $\sqrt2$ at each contrast level (fig. ).
In the cross-frequency condtion at 2 Hz (fig. \@ref(fig:pupildata)d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition. Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig. \@ref(fig:pupildata)e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels. This facilitation is then lost at the highest contrast level, where the amplitude of the monocular signal is equal to the amplitude of the binocular signal. This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils. Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.

Figure \@ref(fig:EEGdata) shows the results for EEG. Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic. 
What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig. \@ref(fig:EEGdata)c) and second (fig. \@ref(fig:EEGdata)f) harmonics are showing very high summation of binocular signals compared to the pupillometry. The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses. This is especially clear at the highest contrasts. This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry. For the cross-frequency condition at 2 Hz and 4 Hz (fig. \@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig. \@ref(fig:EEGdata)e) and 3.2 Hz (fig. \@ref(fig:EEGdata)h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex. 
```{r include=FALSE, results='hide'}

@@

## Experiment 2
The results from the second experiment are shown in \@ref(fig:TFdata). Figure \@ref(fig:TFdata)a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz). We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics. However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded. This is also reflected in figure \@ref(fig:TFdata)b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz. The rest of figure \@ref(fig:TFdata)b is showing the response at each stimulation frequency. We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz. In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig. \@ref(fig:TFdata)c), suggesting that binocular facilitation is happening at higher frequencies. However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \@ref(fig:TFdata)c). The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
```{r include=FALSE, results='hide'}

### 2022-10-04 manuscript.tex
Added experiment 2 results write up

\title{Different rules for binocular combination of luminance in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
\date{2022-09-28}

@@

Figure \ref{fig:pupildata} is showing the results for the pupillometry. Figure \ref{fig:pupildata}a is showing the group average waveform for binocular presentation. Figure \ref{fig:pupildata}b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli. Figures \ref{fig:pupildata}c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz. In the same-frequency condition at 2 Hz (fig.~\ref{fig:pupildata}c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration. In the cross-frequency condtion at 2 Hz (fig.~\ref{fig:pupildata}d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition. Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.~\ref{fig:pupildata}e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels. This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils. Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.

Figure \ref{fig:EEGdata} shows the results for EEG. Figure \ref{fig:EEGdata}a is showing the group average waveform for binocular presentation. Figure \ref{fig:EEGdata}b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \ref{fig:EEGdata}c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \ref{fig:EEGdata}f-h show the CRFs at the second harmonic. What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonic are showing very high summation of binocular signals. The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses. This is especially clear at the highest contrasts. For the cross-frequency condition at 2 Hz and 4 Hz (fig.~\ref{fig:EEGdata}d and \ref{fig:EEGdata}g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig.~\ref{fig:EEGdata}e) and 3.2 Hz (fig.~\ref{fig:EEGdata}h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.

@@

The results from the second experiment are shown in figure \ref{fig:TFdata}. Figure \ref{fig:TFdata}a is showing the fourier spectra

>>>>

\title{Different rules for binocular combination of luminance in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
\date{2022-10-04}

@@

Figure \ref{fig:pupildata} is showing the results for the pupillometry. Figure \ref{fig:pupildata}a is showing the group average waveform for binocular presentation. Figure \ref{fig:pupildata}b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli. Figures \ref{fig:pupildata}c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz. In the same-frequency condition at 2 Hz (fig.~\ref{fig:pupildata}c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration. In general, we observe that the binocular to monocular ratio is roughly \(\sqrt2\) at each contrast level (fig.~).
In the cross-frequency condtion at 2 Hz (fig.~\ref{fig:pupildata}d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition. Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.~\ref{fig:pupildata}e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels. This facilitation is then lost at the highest contrast level, where the amplitude of the monocular signal is equal to the amplitude of the binocular signal. This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils. Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.

Figure \ref{fig:EEGdata} shows the results for EEG. Figure \ref{fig:EEGdata}a is showing the group average waveform for binocular presentation. Figure \ref{fig:EEGdata}b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \ref{fig:EEGdata}c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \ref{fig:EEGdata}f-h show the CRFs at the second harmonic.
What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonics are showing very high summation of binocular signals compared to the pupillometry. The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses. This is especially clear at the highest contrasts. This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry. For the cross-frequency condition at 2 Hz and 4 Hz (fig.~\ref{fig:EEGdata}d and \ref{fig:EEGdata}g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig.~\ref{fig:EEGdata}e) and 3.2 Hz (fig.~\ref{fig:EEGdata}h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.

@@

The results from the second experiment are shown in \ref{fig:TFdata}. Figure \ref{fig:TFdata}a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz). We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics. However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded. This is also reflected in figure \ref{fig:TFdata}b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz. The rest of figure \ref{fig:TFdata}b is showing the response at each stimulation frequency. We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz. In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig.~\ref{fig:TFdata}c), suggesting that binocular facilitation is happening at higher frequencies. However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \ref{fig:TFdata}c). The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
